\textcolor{red}{Simple} connectome inference using partial correlation from imaging calcium signal

### 2014-06-16 article.tex
break line + don't make quation inline

By nature, the firing event is really fast and in order to
retrieve the connectivity from them, it is necessary to link a burst to a
couple of timesteps (ideally one). The small decay for the fluorescent calcium indicator implies a signal
variation during a long time interval. Firing event are represented by strong
variations in the neuron activity. Therefore we apply a hard-tresholding
filter $x^{t,d}_i = x^{t,d}_i \mathbb{1}(x^{t,d}_i \geq \tau)$ where the
threshold $\tau$ should be taken positive and non-close to zero to
respectivelty only keep rising edges and strong variations.

>>>>

By nature, the firing event is really fast and in order to
retrieve the connectivity from them, it is necessary to link a burst to a
couple of timesteps (ideally one). The small decay for the fluorescent calcium
indicator implies a signal
variation during a long time interval. Firing event are represented by strong
variations in the neuron activity. Therefore we apply a hard-tresholding
filter
\begin{align}
x^{t,d}_i &= x^{t,d}_i \mathbb{1}(x^{t,d}_i \geq \tau)
\end{align}
where the threshold $\tau$ should be taken positive and non-close to zero to
respectively only keep rising edges and strong variations.
